Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-08-28 article.tex
ML: edits - up to final todo's

The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes. In Figure \ref{fig:marcel}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used. 
% TODO: the prior sentance is not likely to be understood by a more general audience. also why?
This distinction highlighted how operational decisions can vary based on regional practices and priorities. A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land. However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.

As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture. Climate conditions also play a significant role, influencing water availability, quality and disease/pest pressures. Within both of the models, the most significant factors impacting sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate conditions. These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.

@@

The Coonawarra-specific BNs both support the findings from the literature, with a more structured map of how factors interact compared to the Leximancer summary in Figure \ref{fig:lexi}. The BN provides a detailed view of the relationships between factors, highlighting the central role of water and the interconnectedness of pest management, market pressures, and climate conditions. Additionally, the BNs emphasise economic factors, such as market pressures and grape prices, and includes how they interact within a scope of secondary factors like fuel and electricity use.

@@

\section{Discussion}

This investigation highlights the key factors of Australian winegrowing that contribute to  sustainability through the lens of BNs created with assistance from industry input. These models have established the intricate, and interconnected nature of various influences on sustainability in Australian winegrowing. A keener understanding of how these factors both interact and affect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables. The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture~\cite{chawlaWaterProductivityAgriculture2023}, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~\cite{australianbureauofstatisticsWaterUseAustralian2021}.

@@

The case study highlighted the direct influences on sustainability, where sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}). A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\cite{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}. The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~\cite{baianoOverviewSustainabilityWine2021}.

@@

The BN models helped to illustrate how economic incentives can be drivers of sustainable practices. The definitive influence and relationships between what are more tertiary considerations of sustainability being directly connected to further considerations such as operational costs. Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have an impact on sustainability practices but were limited in this study through only reviewing them within the lens of sustainability. The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers as well as what may be much more specific circumstance; of which is a potential further avenue of research that would compliment this work significantly.

@@

This study provides an in-depth examination of sustainability in Australia and the Coonawarra winegrowing region using BNs. Through integrating industry expertise and empirical data, the BN models developed in this research offered a structured and quantitative framework for understanding the complex interactions amongst key factors influencing sustainability. The findings highlight the critical role of water quality and availability, emphasising its critical influence on all operational decisions either directly or propagating through other factors. With this critical nature being due to water being the most interconnected factor. With this high interrelatedness emphasising the importance efficient water management practices enhancing sustainability in viticulture.

>>>>

The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes. In Figure \ref{fig:marcel}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used. 
% TODO: the prior sentance is not likely to be understood by a more general audience. also why?
This distinction highlighted how operational decisions can vary based on regional practices and priorities. A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense.
% TODO: This requires further explanation.
However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.
% TODO: The other had fewer tractor passes because they performed 2 operations in a single pass. 
% ML: As I read this, I wander whether there was some bias because the group were very attuuned to the data and had a strong preference to efficient management techniques. Im not convinced that this is representative of coonawarra per se.

As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture. Climate conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
% TODO: This is significant...
Within both of the models, the most significant factors impacting sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate conditions. These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.

@@

The Coonawarra-specific BNs both support the findings from the literature, with a more structured map of how factors interact compared to the Leximancer summary in Figure \ref{fig:lexi}. The BN provides a detailed view of the relationships between factors, highlighting the central role of water and the interconnectedness of pest management, market pressures, and climate conditions. Additionally, the BNs emphasise economic factors, such as market pressures and grape prices, and includes how they interact within a scope of secondary factors like fuel and electricity use.
% TODO: Highlight, in the above paragraph, how the BN differs from other BNs

@@

\section{Discussion}
% weather or climate?
This investigation highlights the key factors of Australian winegrowing that contribute to  sustainability through the lens of BNs created with assistance from industry input. These models have established the intricate, and interconnected nature of various influences on sustainability in Australian winegrowing. A keener understanding of how these factors both interact and affect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables.
%TODO: And therefore what to sustainability?
The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture~\cite{chawlaWaterProductivityAgriculture2023}, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~\cite{australianbureauofstatisticsWaterUseAustralian2021}.

@@

The case study highlighted the direct influences on environmental impact, where it was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}). A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\cite{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}. The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~\cite{baianoOverviewSustainabilityWine2021}.

@@

The BN models helped to illustrate how economic incentives can be drivers of sustainable practices. The definitive influence and relationships between what are more tertiary considerations of sustainability being directly connected to further considerations such as operational costs. Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have an impact on sustainability practices but were limited in this study through only reviewing them within the lens of sustainability. The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers as well as what may be much more specific circumstance; of which is a potential further avenue of research that would compliment this work significantly.
% TODO: What do you mean here?

@@

This study provides an in-depth examination of sustainable winegrowing in Australia and the Coonawarra winegrowing region using BNs. Through integrating industry expertise and empirical data, the BN models developed in this research offered a structured and quantitative framework for understanding the complex interactions amongst key factors influencing sustainability. The findings highlight the critical role of water quality and availability, emphasising its critical influence on all operational decisions either directly or propagating through other factors. With this critical nature being due to water being the most interconnected factor, emphasising the importance efficient water management practices enhancing sustainability in viticulture.
